The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-15 analysis/paper/paper.qmd
Updarte preview code chunk

# Preview theses
emu_theses %>% 
  arrange(graduation_year) %>% 
  pull(text_clean) %>% 
  str_sub(1, 500)

# Preview theses
hist(str_length(emu_theses$text_clean))

Encoding(emu_theses$text_clean)
```

@@

# Add latitude and longitude information to theses data frame
emu_theses <- geocode_thesis_locations(emu_theses)

# Show thesis locations on world map
visualize_thesis_locations(emu_theses)
```

>>>>

# Preview theses in increasing order of graduation year
emu_theses %>% 
  arrange(graduation_year) %>% 
  pull(text_clean) %>% 
  head_text(head_n = 5)

# Show distribution of the length of theses
hist(str_length(emu_theses$text_clean))
```

@@

# Geocode thesis locations
emu_theses <- emu_theses %>%
  geocode(location, method = 'osm', lat = latitude , long = longitude)

# Show thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_point(data = emu_theses, aes(longitude, latitude), color = "red") +
  coord_fixed() +
  theme_void()
```
